\textit{F1000Research} A studyforrest extension, an annotations of words and phonemes in the German dubbed movie ``Forrest Gump'' and its audio-description

### 2020-04-03 paper/main.tex
add preliminary tables to main.tex

% For more detailed article preparation guidelines, please see:
% http://f1000research.com/author-guidelines
\documentclass[10pt,a4paper,twocolumn]{article}
\usepackage{f1000_styles}
\usepackage[
	colorlinks=true,
	urlcolor=blue,
	linkcolor=green
]{hyperref}
%% Default: numerical citations
\usepackage[numbers]{natbib}

@@

\begin{document}

@@

@@

\subsubsection*{Detailed part-of-speech tag (\texttt{tag})}
A detailed part-of-speech tagging following the TIGER Treebank annotation scheme \citep{brants2004tiger} which is based on the \href{https://www.ims.uni-stuttgart.de/forschung/ressourcen/lexika/germantagsets}{Stuttgart-Tübingen-Tagset} \citep{schiller1999stts}.
\subsubsection*{Syntactic dependency (\texttt{dep})}
A word's column entry provides information about a word's syntactic dependency. Information following the TIGER Treebank annotation scheme \citep{brants2004tiger} is given in the format:
"arc label;word's head;word's child1, word's child2, ..." where the "arc label" describes the type of syntactic relation that connects a "child" (the single word) to its "head".
\subsubsection*{Lemmatization (\texttt{lemma})}
For single words, the base form (root) of the word
\subsubsection*{Common Word (\texttt{stop})}
For single words, this column provides information if the word is part of a stop list, hence one of the most common words in the German language ("True") or not ('"False")?
\subsubsection*{Narrator's descriptive nouns (\texttt{descr})}
A categorizing of nouns that serve as auditory cues about the movie's visual content. Comprised categories focus on the cinematographic scene's environment (geo, geo-room; setting\_new, setting\_old), inherent persons (female, female name; male, male name, person), their appearance (face, head; body, bodypart), and objects (object, furniture).
\paragraph*{Narrator's descriptive nouns}
\begin{center}
\begin{tabular}{ |c|c|c|c| }
\hline
category & description & examples & count\\
\hline
geo & immobile landmarks & building, tree, street, alley, meadow, cornfield, river & 125\\
geo-room & rooms / locales; elements defining a locale's spatial layout & living room; wall, door, window, floor, turf & 105\\
setting\_new & first-time mentioned setting & on a bridge, on an alley, on campus & 86\\
setting\_rec & recurring setting & at the bus stop & 37\\
body & trunk of the body; overlaid clothes & back, hip, shoulder; jacket, dress, shirt & 66\\
bodypart & limbs and trousers & arm, finger, leg, toe & 69\\
face & face or parts of it & face, ear, nose, mouth & 47\\
head & non-face parts of the head; worn headgear & head, hair, ear, neck, helmet & 36\\
furniture & movable objects insides/outsides & bench, bed, table, chair & 50\\
object & countable entities with firm boundaries & feather, telephone, car & 232\\
objects & countable entities with firm boundaries & wheels, photos & 52\\
female & female person & nurse, mother, women & 31\\
females & female persons & women & 3\\
fname & female name & Jenny, Carla & 74\\
male & male person & man, father, soldier & 89\\
males & concrete male persons & boys, opponents & 23\\
mname & male name of person present in the scene & Forrest, Bubba, Kennedy & 291\\
persons & concrete persons of unknown sex / gender & hippies, patients & 17\\
++ & nouns, adverbial adjectives, and adverbs & in the evening, it's daytime, later
\\
\hline
\end{tabular}
\end{center}

\subsubsection*{Word embedding (semantic similarity) (\texttt{vector})}
A word's column entry contains a 300-dimensional \href{https://en.wikipedia.org/wiki/Word2vec}{word vector} providing a multi-dimensional meaning representation of the word. Uncommon and out-of-vocabulary words with a vector consisting of 300 dimensions of 0's were set to '\#' [to save space].

>>>>

% For more detailed article preparation guidelines, please see:
% http://f1000research.com/author-guidelines
\documentclass[10pt,a4paper,twocolumn]{article}
\usepackage{f1000_styles}
\usepackage{booktabs}
\usepackage[
	colorlinks=true,
	urlcolor=blue,
	linkcolor=green
]{hyperref}
%% Default: numerical citations
\usepackage[numbers]{natbib}

@@

\begin{document}
\input{descr-stats-anno.tex}
\input{descr-stats-regressors.tex}

@@

\clearpage
\begin{table*}[t]
\caption{Overview of the speech annotation's content for the whole stimulus and it's individual segments. Words include \aPosNonspeechAll\space non-speech vocalizations.}
\label{tab:example}
\begin{tabular}{llllllllll}
\toprule
\textbf{category} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8}\\
\midrule
sentences  & \aSentencesAll & \aSentencesI & \aSentencesII & \aSentencesIII & \aSentencesIV & \aSentencesV & \aSentencesVI & \aSentencesVII & \aSentencesVIII \tabularnewline
words  & \aWordsAll & \aWordsI & \aWordsII & \aWordsIII & \aWordsIV & \aWordsV & \aWordsVI & \aWordsVII & \aWordsVIII \tabularnewline
phonemes  & \aPhonesAll & \aPhonesI & \aPhonesII & \aPhonesIII & \aPhonesIV & \aPhonesV & \aPhonesVI & \aPhonesVII & \aPhonesVIII \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

\begin{table*}[t]
\caption{Sentences spoken by top 10 of 97 (identified) speakers sorted alphabetically. Narrator only in audio-description.}
\label{tab:example}
\begin{tabular}{llllllllll}
\toprule
\textbf{name} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8}\\
\midrule
Bubba  & \aBubbaAll & \aBubbaI & \aBubbaII & \aBubbaIII & \aBubbaIV & \aBubbaV & \aBubbaVI & \aBubbaVII & \aBubbaVIII \tabularnewline
Forrest  & \aForrestAll & \aForrestI & \aForrestII & \aForrestIII & \aForrestIV & \aForrestV & \aForrestVI & \aForrestVII & \aForrestVIII \tabularnewline
Forrest (child)  & \aForrestchildAll & \aForrestchildI & \aForrestchildII & \aForrestchildIII & \aForrestchildIV & \aForrestchildV & \aForrestchildVI & \aForrestchildVII & \aForrestchildVIII \tabularnewline
Forrest (v.o.)  & \aForrestvoAll & \aForrestvoI & \aForrestvoII & \aForrestvoIII & \aForrestvoIV & \aForrestvoV & \aForrestvoVI & \aForrestvoVII & \aForrestvoVIII \tabularnewline
Hancock  & \aHancockAll & \aHancockI & \aHancockII & \aHancockIII & \aHancockIV & \aHancockV & \aHancockVI & \aHancockVII & \aHancockVIII \tabularnewline
Jenny  & \aJennyAll & \aJennyI & \aJennyII & \aJennyIII & \aJennyIV & \aJennyV & \aJennyVI & \aJennyVII & \aJennyVIII \tabularnewline
Jenny (child)  & \aJennychildAll & \aJennychildI & \aJennychildII & \aJennychildIII & \aJennychildIV & \aJennychildV & \aJennychildVI & \aJennychildVII & \aJennychildVIII \tabularnewline
Lt. Dan  & \aLtdanAll & \aLtdanI & \aLtdanII & \aLtdanIII & \aLtdanIV & \aLtdanV & \aLtdanVI & \aLtdanVII & \aLtdanVIII \tabularnewline
Mrs. Gump  & \aMrsgumpAll & \aMrsgumpI & \aMrsgumpII & \aMrsgumpIII & \aMrsgumpIV & \aMrsgumpV & \aMrsgumpVI & \aMrsgumpVII & \aMrsgumpVIII \tabularnewline
Narrator  & \aNarratorAll & \aNarratorI & \aNarratorII & \aNarratorIII & \aNarratorIV & \aNarratorV & \aNarratorVI & \aNarratorVII & \aNarratorVIII \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

\begin{table*}[t]
\caption{Simple part of speech tagging (POS). All 15 categories sorted alpapetically. Descriptions were taken from spaCy.explain(). Non-speech vocalizations (NONSPEECH) were manually added.}
\label{tab:example}
\begin{tabular}{lllllllllll}
\toprule
\textbf{category} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} & \textbf{description}\\
\midrule
ADJ & \aPosAdjAll & \aPosAdjI & \aPosAdjII & \aPosAdjIII & \aPosAdjIV & \aPosAdjV & \aPosAdjVI & \aPosAdjVII & \aPosAdjVIII & \aPosAdj \tabularnewline
ADP & \aPosAdpAll & \aPosAdpI & \aPosAdpII & \aPosAdpIII & \aPosAdpIV & \aPosAdpV & \aPosAdpVI & \aPosAdpVII & \aPosAdpVIII & \aPosAdp\tabularnewline
ADV & \aPosAdvAll & \aPosAdvI & \aPosAdvII & \aPosAdvIII & \aPosAdvIV & \aPosAdvV & \aPosAdvVI & \aPosAdvVII & \aPosAdvVIII & \aPosAdv\tabularnewline
AUX & \aPosAuxAll & \aPosAuxI & \aPosAuxII & \aPosAuxIII & \aPosAuxIV & \aPosAuxV & \aPosAuxVI & \aPosAuxVII & \aPosAuxVIII & \aPosAux\tabularnewline
CONJ & \aPosConjAll & \aPosConjI & \aPosConjII & \aPosConjIII & \aPosConjIV & \aPosConjV & \aPosConjVI & \aPosConjVII & \aPosConjVIII & \aPosConj \tabularnewline
DET & \aPosDetAll & \aPosDetI & \aPosDetII & \aPosDetIII & \aPosDetIV & \aPosDetV & \aPosDetVI & \aPosDetVII & \aPosDetVIII & \aPosDet\tabularnewline
NONSPEECH  & \aPosNonspeechAll & \aPosNonspeechI & \aPosNonspeechII & \aPosNonspeechIII & \aPosNonspeechIV & \aPosNonspeechV & \aPosNonspeechVI & \aPosNonspeechVII & \aPosNonspeechVIII & non-speech vocalization \tabularnewline
NOUN & \aPosNounAll & \aPosNounI & \aPosNounII & \aPosNounIII & \aPosNounIV & \aPosNounV & \aPosNounVI & \aPosNounVII & \aPosNounVIII & \aPosNoun \tabularnewline
NUM & \aPosNumAll & \aPosNumI & \aPosNumII & \aPosNumIII & \aPosNumIV & \aPosNumV & \aPosNumVI & \aPosNumVII & \aPosNumVIII & \aPosNum\tabularnewline
PART & \aPosPartAll & \aPosPartI & \aPosPartII & \aPosPartIII & \aPosPartIV & \aPosPartV & \aPosPartVI & \aPosPartVII & \aPosPartVIII & \aPosPart \tabularnewline
PRON & \aPosPronAll & \aPosPronI & \aPosPronII & \aPosPronIII & \aPosPronIV & \aPosPronV & \aPosPronVI & \aPosPronVII & \aPosPronVIII & \aPosPron \tabularnewline
PRON  & \aPosPropnAll & \aPosPropnI & \aPosPropnII & \aPosPropnIII & \aPosPropnIV & \aPosPropnV & \aPosPropnVI & \aPosPropnVII & \aPosPropnVIII & \aPosPropn \tabularnewline
SCONJ & \aPosSconjAll & \aPosSconjI & \aPosSconjII & \aPosSconjIII & \aPosSconjIV & \aPosSconjV & \aPosSconjVI & \aPosSconjVII & \aPosSconjVIII & \aPosSconj \tabularnewline
VERB & \aPosVerbAll & \aPosVerbI & \aPosVerbII & \aPosVerbIII & \aPosVerbIV & \aPosVerbV & \aPosVerbVI & \aPosVerbVII & \aPosVerbVIII & \aPosVerb\tabularnewline
X & \aPosXAll & \aPosXI & \aPosXII & \aPosXIII & \aPosXIV & \aPosXV & \aPosXVI & \aPosXVII & \aPosXVIII & \aPosX \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

\begin{table*}[t]
\caption{Detailed part of speech tagging (TAG). The top 15 of 43 categories sorted alphabetically. Descriptions were taken from spaCy.explain().}
\label{tab:example}
\begin{tabular}{lllllllllll}
\toprule
\textbf{category} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} & \textbf{description}\\
\midrule
ADJA  & \aTagAdjaAll & \aTagAdjaI & \aTagAdjaII & \aTagAdjaIII & \aTagAdjaIV & \aTagAdjaV & \aTagAdjaVI & \aTagAdjaVII & \aTagAdjaVIII & \aTagAdja \tabularnewline
ADJD  & \aTagAdjdAll & \aTagAdjdI & \aTagAdjdII & \aTagAdjdIII & \aTagAdjdIV & \aTagAdjdV & \aTagAdjdVI & \aTagAdjdVII & \aTagAdjdVIII & \aTagAdjd \tabularnewline
ADV  & \aTagAdvAll & \aTagAdvI & \aTagAdvII & \aTagAdvIII & \aTagAdvIV & \aTagAdvV & \aTagAdvVI & \aTagAdvVII & \aTagAdvVIII & \aTagAdv \tabularnewline
APPR  & \aTagApprAll & \aTagApprI & \aTagApprII & \aTagApprIII & \aTagApprIV & \aTagApprV & \aTagApprVI & \aTagApprVII & \aTagApprVIII & \aTagAppr \tabularnewline
ART  & \aTagArtAll & \aTagArtI & \aTagArtII & \aTagArtIII & \aTagArtIV & \aTagArtV & \aTagArtVI & \aTagArtVII & \aTagArtVIII & \aTagArt \tabularnewline
KON  & \aTagKonAll & \aTagKonI & \aTagKonII & \aTagKonIII & \aTagKonIV & \aTagKonV & \aTagKonVI & \aTagKonVII & \aTagKonVIII & \aTagKon \tabularnewline
NE  & \aTagNeAll & \aTagNeI & \aTagNeII & \aTagNeIII & \aTagNeIV & \aTagNeV & \aTagNeVI & \aTagNeVII & \aTagNeVIII & \aTagNe \tabularnewline
NN  & \aTagNnAll & \aTagNnI & \aTagNnII & \aTagNnIII & \aTagNnIV & \aTagNnV & \aTagNnVI & \aTagNnVII & \aTagNnVIII & \aTagNn \tabularnewline
PPER  & \aTagPperAll & \aTagPperI & \aTagPperII & \aTagPperIII & \aTagPperIV & \aTagPperV & \aTagPperVI & \aTagPperVII & \aTagPperVIII & \aTagPper \tabularnewline
PPOSAT  & \aTagPposatAll & \aTagPposatI & \aTagPposatII & \aTagPposatIII & \aTagPposatIV & \aTagPposatV & \aTagPposatVI & \aTagPposatVII & \aTagPposatVIII & \aTagPposat \tabularnewline
PTKVZ  & \aTagPtkvzAll & \aTagPtkvzI & \aTagPtkvzII & \aTagPtkvzIII & \aTagPtkvzIV & \aTagPtkvzV & \aTagPtkvzVI & \aTagPtkvzVII & \aTagPtkvzVIII & \aTagPtkvz \tabularnewline
VAFIN  & \aTagVafinAll & \aTagVafinI & \aTagVafinII & \aTagVafinIII & \aTagVafinIV & \aTagVafinV & \aTagVafinVI & \aTagVafinVII & \aTagVafinVIII & \aTagVafin \tabularnewline
VVFIN  & \aTagVvfinAll & \aTagVvfinI & \aTagVvfinII & \aTagVvfinIII & \aTagVvfinIV & \aTagVvfinV & \aTagVvfinVI & \aTagVvfinVII & \aTagVvfinVIII & \aTagVvfin \tabularnewline
VVINF  & \aTagVvinfAll & \aTagVvinfI & \aTagVvinfII & \aTagVvinfIII & \aTagVvinfIV & \aTagVvinfV & \aTagVvinfVI & \aTagVvinfVII & \aTagVvinfVIII & \aTagVvinf \tabularnewline
VVPP  & \aTagVvppAll & \aTagVvppI & \aTagVvppII & \aTagVvppIII & \aTagVvppIV & \aTagVvppV & \aTagVvppVI & \aTagVvppVII & \aTagVvppVIII & \aTagVvpp \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

\begin{table*}[t]
\caption{Syntactic dependencies (DEP). The top 15 of 37 categories sorted alphabetically. Descriptions were taken from spaCy.explain().}
\label{tab:example}
\begin{tabular}{lllllllllll}
\toprule
\textbf{category} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} & \textbf{description}\\
\midrule
cd  & \aDepCdAll & \aDepCdI & \aDepCdII & \aDepCdIII & \aDepCdIV & \aDepCdV & \aDepCdVI & \aDepCdVII & \aDepCdVIII & \aDepCd \tabularnewline
cj  & \aDepCjAll & \aDepCjI & \aDepCjII & \aDepCjIII & \aDepCjIV & \aDepCjV & \aDepCjVI & \aDepCjVII & \aDepCjVIII & \aDepCj \tabularnewline
cp  & \aDepCpAll & \aDepCpI & \aDepCpII & \aDepCpIII & \aDepCpIV & \aDepCpV & \aDepCpVI & \aDepCpVII & \aDepCpVIII & \aDepCp \tabularnewline
da  & \aDepDaAll & \aDepDaI & \aDepDaII & \aDepDaIII & \aDepDaIV & \aDepDaV & \aDepDaVI & \aDepDaVII & \aDepDaVIII & \aDepDa \tabularnewline
ju  & \aDepJuAll & \aDepJuI & \aDepJuII & \aDepJuIII & \aDepJuIV & \aDepJuV & \aDepJuVI & \aDepJuVII & \aDepJuVIII & \aDepJu \tabularnewline
mnr  & \aDepMnrAll & \aDepMnrI & \aDepMnrII & \aDepMnrIII & \aDepMnrIV & \aDepMnrV & \aDepMnrVI & \aDepMnrVII & \aDepMnrVIII & \aDepMnr \tabularnewline
Mmo  & \aDepMoAll & \aDepMoI & \aDepMoII & \aDepMoIII & \aDepMoIV & \aDepMoV & \aDepMoVI & \aDepMoVII & \aDepMoVIII & \aDepMo \tabularnewline
nk  & \aDepNkAll & \aDepNkI & \aDepNkII & \aDepNkIII & \aDepNkIV & \aDepNkV & \aDepNkVI & \aDepNkVII & \aDepNkVIII & \aDepNk \tabularnewline
oa  & \aDepOaAll & \aDepOaI & \aDepOaII & \aDepOaIII & \aDepOaIV & \aDepOaV & \aDepOaVI & \aDepOaVII & \aDepOaVIII & \aDepOa \tabularnewline
oc  & \aDepOcAll & \aDepOcI & \aDepOcII & \aDepOcIII & \aDepOcIV & \aDepOcV & \aDepOcVI & \aDepOcVII & \aDepOcVIII & \aDepOc \tabularnewline
pd  & \aDepPdAll & \aDepPdI & \aDepPdII & \aDepPdIII & \aDepPdIV & \aDepPdV & \aDepPdVI & \aDepPdVII & \aDepPdVIII & \aDepPd \tabularnewline
pnc  & \aDepPncAll & \aDepPncI & \aDepPncII & \aDepPncIII & \aDepPncIV & \aDepPncV & \aDepPncVI & \aDepPncVII & \aDepPncVIII & \aDepPnc \tabularnewline
ROOT  & \aDepRootAll & \aDepRootI & \aDepRootII & \aDepRootIII & \aDepRootIV & \aDepRootV & \aDepRootVI & \aDepRootVII & \aDepRootVIII & root \tabularnewline
sb  & \aDepSbAll & \aDepSbI & \aDepSbII & \aDepSbIII & \aDepSbIV & \aDepSbV & \aDepSbVI & \aDepSbVII & \aDepSbVIII & \aDepSb \tabularnewline
svp  & \aDepSvpAll & \aDepSvpI & \aDepSvpII & \aDepSvpIII & \aDepSvpIV & \aDepSvpV & \aDepSvpVI & \aDepSvpVII & \aDepSvpVIII & separable verb prefix \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

\begin{table*}[t]
    \caption{Narrator's descriptive nouns. All categories sorted alphapetically. Examples are given in English. Description (of rules) fehlt in dieser Tabelle (vgl. alte Tabelle auf der allerletzten Seite). Wird nämlich in einer Tabelle mit horizontaler Ausrichtung eng. Kategorie ```++''' enthält ausnahmesweise auch adverbiale Best. der Zeit'''.}
\label{tab:example}
\begin{tabular}{lllllllllll}
\toprule
\textbf{category} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} &     \textbf{examples}\\
\midrule
body & \aDescrBodyAll & \aDescrBodyI & \aDescrBodyII & \aDescrBodyIII & \aDescrBodyIV & \aDescrBodyV & \aDescrBodyVI & \aDescrBodyVII & \aDescrBodyVIII & back, hip, shoulder; jacket, dress, shirt \tabularnewline
bodypart & \aDescrBodypartAll & \aDescrBodypartI & \aDescrBodypartII & \aDescrBodypartIII & \aDescrBodypartIV & \aDescrBodypartV & \aDescrBodypartVI & \aDescrBodypartVII & \aDescrBodypartVIII & arm, finger, leg, toe \tabularnewline
face  & \aDescrFaceAll & \aDescrFaceI & \aDescrFaceII & \aDescrFaceIII & \aDescrFaceIV & \aDescrFaceV & \aDescrFaceVI & \aDescrFaceVII & \aDescrFaceVIII & face, ear, nose, mouth \tabularnewline
female  & \aDescrFemaleAll & \aDescrFemaleI & \aDescrFemaleII & \aDescrFemaleIII & \aDescrFemaleIV & \aDescrFemaleV & \aDescrFemaleVI & \aDescrFemaleVII & \aDescrFemaleVIII & nurse, mother, woman \tabularnewline
females  & \aDescrFemalesAll & \aDescrFemalesI & \aDescrFemalesII & \aDescrFemalesIII & \aDescrFemalesIV & \aDescrFemalesV & \aDescrFemalesVI & \aDescrFemalesVII & \aDescrFemalesVIII & women \tabularnewline
fname  & \aDescrFnameAll & \aDescrFnameI & \aDescrFnameII & \aDescrFnameIII & \aDescrFnameIV & \aDescrFnameV & \aDescrFnameVI & \aDescrFnameVII & \aDescrFnameVIII & Jenny \tabularnewline
furniture  & \aDescrFurnitureAll & \aDescrFurnitureI & \aDescrFurnitureII & \aDescrFurnitureIII & \aDescrFurnitureIV & \aDescrFurnitureV & \aDescrFurnitureVI & \aDescrFurnitureVII & \aDescrFurnitureVIII & bench, bed, table, chair \tabularnewline
geo  & \aDescrGeoAll & \aDescrGeoI & \aDescrGeoII & \aDescrGeoIII & \aDescrGeoIV & \aDescrGeoV & \aDescrGeoVI & \aDescrGeoVII & \aDescrGeoVIII & building, tree, street, alley, meadow, cornfield, river \tabularnewline
geo-room  & \aDescrGeoroomAll & \aDescrGeoroomI & \aDescrGeoroomII & \aDescrGeoroomIII & \aDescrGeoroomIV & \aDescrGeoroomV & \aDescrGeoroomVI & \aDescrGeoroomVII & \aDescrGeoroomVIII & living room; wall, door, window, floor, turf \tabularnewline
head  & \aDescrHeadAll & \aDescrHeadI & \aDescrHeadII & \aDescrHeadIII & \aDescrHeadIV & \aDescrHeadV & \aDescrHeadVI & \aDescrHeadVII & \aDescrHeadVIII & head, hair, ear, neck, helmet \tabularnewline
male  & \aDescrMaleAll & \aDescrMaleI & \aDescrMaleII & \aDescrMaleIII & \aDescrMaleIV & \aDescrMaleV & \aDescrMaleVI & \aDescrMaleVII & \aDescrMaleVIII & man, father, soldier \tabularnewline
males  & \aDescrMalesAll & \aDescrMalesI & \aDescrMalesII & \aDescrMalesIII & \aDescrMalesIV & \aDescrMalesV & \aDescrMalesVI & \aDescrMalesVII & \aDescrMalesVIII & boys, opponents \tabularnewline
mname  & \aDescrMnameAll & \aDescrMnameI & \aDescrMnameII & \aDescrMnameIII & \aDescrMnameIV & \aDescrMnameV & \aDescrMnameVI & \aDescrMnameVII & \aDescrMnameVIII & Bubba, Kennedy \tabularnewline
object  & \aDescrObjectAll & \aDescrObjectI & \aDescrObjectII & \aDescrObjectIII & \aDescrObjectIV & \aDescrObjectV & \aDescrObjectVI & \aDescrObjectVII & \aDescrObjectVIII & telephone, car \tabularnewline
objects  & \aDescrObjectsAll & \aDescrObjectsI & \aDescrObjectsII & \aDescrObjectsIII & \aDescrObjectsIV & \aDescrObjectsV & \aDescrObjectsVI & \aDescrObjectsVII & \aDescrObjectsVIII & wheels, photos \tabularnewline
persons  & \aDescrPersonsAll & \aDescrPersonsI & \aDescrPersonsII & \aDescrPersonsIII & \aDescrPersonsIV & \aDescrPersonsV & \aDescrPersonsVI & \aDescrPersonsVII & \aDescrPersonsVIII & hippies, patients \tabularnewline
setting\_new  & \aDescrSettingnewAll & \aDescrSettingnewI & \aDescrSettingnewII & \aDescrSettingnewIII & \aDescrSettingnewIV & \aDescrSettingnewV & \aDescrSettingnewVI & \aDescrSettingnewVII & \aDescrSettingnewVIII & on a ```bridge''', on an ```alley''', on ```campus''' \tabularnewline
setting\_rec  & \aDescrSettingrecAll & \aDescrSettingrecI & \aDescrSettingrecII & \aDescrSettingrecIII & \aDescrSettingrecIV & \aDescrSettingrecV & \aDescrSettingrecVI & \aDescrSettingrecVII & \aDescrSettingrecVIII & at the ```bus stop''' \tabularnewline
++  & \aDescrAll & \aDescrI & \aDescrII & \aDescrIII & \aDescrIV & \aDescrV & \aDescrVI & \aDescrVII & \aDescrVIII & in the ```evening''', it's ```daytime''', ```later''' \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

\begin{table*}[t]
\caption{Overview of the 26 REGRESSORS used for the validation analysis. The top 20 categories of the detailed part-of speech tagging were used as such. Descriptions were taken from spaCy.explain(). All others tags were pooled to ```tag\_other'''. The other categories were build\dots}
\label{tab:example}
\begin{tabular}{llllllllllll}
\toprule
\textbf{no} & \textbf{name} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} & \textbf{description}\\
\midrule
1 & adja  & \rAdjaAll & \rAdjaI & \rAdjaII & \rAdjaIII & \rAdjaIV & \rAdjaV & \rAdjaVI & \rAdjaVII & \rAdjaVIII & \aTagAdja \tabularnewline
2 & adjd  & \rAdjdAll & \rAdjdI & \rAdjdII & \rAdjdIII & \rAdjdIV & \rAdjdV & \rAdjdVI & \rAdjdVII & \rAdjdVIII & \aTagAdjd \tabularnewline
3 & adv  & \rAdvAll & \rAdvI & \rAdvII & \rAdvIII & \rAdvIV & \rAdvV & \rAdvVI & \rAdvVII & \rAdvVIII & \aTagAdv \tabularnewline
4 & appr  & \rApprAll & \rApprI & \rApprII & \rApprIII & \rApprIV & \rApprV & \rApprVI & \rApprVII & \rApprVIII & \aTagAppr \tabularnewline
5 & apprart  & \rApprartAll & \rApprartI & \rApprartII & \rApprartIII & \rApprartIV & \rApprartV & \rApprartVI & \rApprartVII & \rApprartVIII & preposition with article \tabularnewline
6 & art  & \rArtAll & \rArtI & \rArtII & \rArtIII & \rArtIV & \rArtV & \rArtVI & \rArtVII & \rArtVIII & \aTagArt \tabularnewline
7 & kon  & \rKonAll & \rKonI & \rKonII & \rKonIII & \rKonIV & \rKonV & \rKonVI & \rKonVII & \rKonVIII & \aTagKon \tabularnewline
8 & ne  & \rNeAll & \rNeI & \rNeII & \rNeIII & \rNeIV & \rNeV & \rNeVI & \rNeVII & \rNeVIII & \aTagNe \tabularnewline
9 & nn  & \rNnAll & \rNnI & \rNnII & \rNnIII & \rNnIV & \rNnV & \rNnVI & \rNnVII & \rNnVIII & \aTagNn \tabularnewline
10 & pds  & \rPdsAll & \rPdsI & \rPdsII & \rPdsIII & \rPdsIV & \rPdsV & \rPdsVI & \rPdsVII & \rPdsVIII & substituting demonstrative pronoun \tabularnewline
11 & pis  & \rPisAll & \rPisI & \rPisII & \rPisIII & \rPisIV & \rPisV & \rPisVI & pper \rPisVII & \rPisVIII & substituting indefinite pronou \tabularnewline
12 & pper  & \rPperAll & \rPperI & \rPperII & \rPperIII & \rPperIV & \rPperV & \rPperVI & \rPperVII & \rPperVIII & \aTagPper \tabularnewline
13 & pposat & \rPposatAll & \rPposatI & \rPposatII & \rPposatIII & \rPposatIV & \rPposatV & \rPposatVI & \rPposatVII & \rPposatVIII & \aTagPposat \tabularnewline
14 & prf  & \rPrfAll & \rPrfI & \rPrfII & \rPrfIII & \rPrfIV & \rPrfV & \rPrfVI & \rPrfVII & \rPrfVIII & reflexive personal pronoun \tabularnewline
15 & ptkvz  & \rPtkvzAll & \rPtkvzI & \rPtkvzII & \rPtkvzIII & \rPtkvzIV & \rPtkvzV & \rPtkvzVI & \rPtkvzVII & \rPtkvzVIII & \aTagPtkvz \tabularnewline
16 & vafin  & \rVafinAll & \rVafinI & \rVafinII & \rVafinIII & \rVafinIV & \rVafinV & \rVafinVI & \rVafinVII & \rVafinVIII & \aTagVafin \tabularnewline
17 & vmfin  & \rVmfinAll & \rVmfinI & \rVmfinII & \rVmfinIII & \rVmfinIV & \rVmfinV & \rVmfinVI & \rVmfinVII & \rVmfinVIII & finite verb, modal \tabularnewline
18 & vvfin  & \rVvfinAll & \rVvfinI & \rVvfinII & \rVvfinIII & \rVvfinIV & \rVvfinV & \rVvfinVI & \rVvfinVII & \rVvfinVIII & \aTagVvfin \tabularnewline
19 & vvinf  & \rVvinfAll & \rVvinfI & \rVvinfII & \rVvinfIII & \rVvinfIV & \rVvinfV & \rVvinfVI & \rVvinfVII & \rVvinfVIII & \aTagVvinf \tabularnewline
20 & vvpp  & \rVvppAll & \rVvppI & \rVvppII & \rVvppIII & \rVvppIV & \rVvppV & \rVvppVI & \rVvppVII & \rVvppVIII & \aTagVvpp \tabularnewline
21 & tag\_other  & \rTagotherAll & \rTagotherI & \rTagotherII & \rTagotherIII & \rTagotherIV & \rTagotherV & \rTagotherVI & \rTagotherVII & \rTagotherVIII & all other TAG categories \tabularnewline
22 & sentence  & \rSentenceAll & \rSentenceI & \rSentenceII & \rSentenceIII & \rSentenceIV & \rSentenceV & \rSentenceVI & \rSentenceVII & \rSentenceVIII & complete grammatical sentences \tabularnewline
23 & phones  & \rPhonesAll & \rPhonesI & \rPhonesII & \rPhonesIII & \rPhonesIV & \rPhonesV & \rPhonesVI & \rPhonesVII & \rPhonesVIII & top XY phonemes \tabularnewline
24 & no-sp  & \rNospAll & \rNospI & \rNospII & \rNospIII & \rNospIV & \rNospV & \rNospVI & \rNospVII & \rNospVIII & no speech (```soundscape''') \tabularnewline
25 & fg\_ad\_lrdiff  & \rFgadlrdiffAll & \rFgadlrdiffI & \rFgadlrdiffII & \rFgadlrdiffIII & \rFgadlrdiffIV & \rFgadlrdiffV & \rFgadlrdiffVI & \rFgadlrdiffVII & \rFgadlrdiffVIII & left-right volume difference \tabularnewline
26 & fg\_ad\_rms  & \rFgadrmsAll & \rFgadrmsI & \rFgadrmsII & \rFgadrmsIII & \rFgadrmsIV & \rFgadrmsV & \rFgadrmsVI & \rFgadrmsVII & \rFgadrmsVIII & root mean square \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

@@

\subsubsection*{Detailed part-of-speech tag (\texttt{tag})}
A detailed part-of-speech tagging following the TIGER Treebank annotation scheme \citep{brants2004tiger} which is based on the \href{https://www.ims.uni-stuttgart.de/forschung/ressourcen/lexika/germantagsets}{Stuttgart-Tübingen-Tagset} \citep{schiller1999stts}.
\subsubsection*{Syntactic dependency (\texttt{dep})}
A word's column entry provides information about a word's syntactic dependency. Information following the TIGER Treebank annotation scheme \citep{brants2004tiger} is given in the format:
"arc label;word's head;word's child1, word's child2, ..." where the "arc label" describes the type of syntactic relation that connects a "child" (the single word) to its "head".
\subsubsection*{Lemmatization (\texttt{lemma})}
For single words, the base form (root) of the word
\subsubsection*{Common Word (\texttt{stop})}
For single words, this column provides information if the word is part of a stop list, hence one of the most common words in the German language ("True") or not ('"False")?
\subsubsection*{Narrator's descriptive nouns (\texttt{descr})}
A categorizing of nouns that serve as auditory cues about the movie's visual content. Comprised categories focus on the cinematographic scene's environment (geo, geo-room; setting\_new, setting\_old), inherent persons (female, female name; male, male name, person), their appearance (face, head; body, bodypart), and objects (object, furniture).
\paragraph*{Narrator's descriptive nouns}
\subsubsection*{Word embedding (semantic similarity) (\texttt{vector})}
A word's column entry contains a 300-dimensional \href{https://en.wikipedia.org/wiki/Word2vec}{word vector} providing a multi-dimensional meaning representation of the word. Uncommon and out-of-vocabulary words with a vector consisting of 300 dimensions of 0's were set to '\#' [to save space].
